Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
DONE

    \par In this model, instead of giving citizens particular evacuation plan, we give them a simple rule: move directly away from the hurricane landfall if possible, else move North or North-West. Using the statewide broadcast system, the state of Mississippi can tell its citizens where the expected landfall will be, and which counties will be the most affected. In which case, individual citizens are instructed to leave the counties that will be flooded, and to do so as outlined above. This means less coordination from the state, and more options for each citizens. At the cost of not having designated areas, and therefore designated refuge areas for citizens, evacuation is faster because it involves less per-county organization.\\

@@

\section{Individual Contributions}
\label{sec:contributions}
\subsection*{Ryan}
Performed the data-fetching of the hurricanes. Wrote all of the most of the manuscript with Paul. Worked out some of the logic for both the flow and the Markov model.

\subsection*{Paul}
Designed and implemented the stochastic model. Helped Ryan write most of the manuscript. Parsed the county data such as county location and population using the WolframAlpha API. Created the Mississippi Highway map used in all the models.

\subsection*{Antoine}
Implemented the flow and Markov models. Created almost all of the graph and network visualizations. Worked on the two first models' analyses for the manuscript. Wrote the Future Work section and the Individual Contributions.

>>>>

    \par In this model, instead of giving citizens particular evacuation plan, we give them a simple rule: move directly away from the hurricane landfall if possible, else move North or North-West. Using and assumed statewide broadcast system, the state of Mississippi can tell its citizens where the expected landfall will be, and which counties will be the most affected. In which case, individual citizens are instructed to leave the counties that will be flooded, and to do so as outlined above. This means less coordination from the state, and more options for each citizens. At the cost of not having designated areas, and therefore designated refuge areas for citizens, evacuation is faster because it involves less per-county organization.\\

@@

\section{Individual Contributions}
\label{sec:contributions}
\subsection*{Ryan}
Performed analysis of historical hurricane data. Contributed to writing and revision of the manuscript. Helped to work out the design and logic for both the MaxFlow and the Markov model.

\subsection*{Paul}
Designed and implemented the stochastic model. Helped Ryan write the manuscript. Parsed the county data such as county location and population using the WolframAlpha API. Created the Mississippi Highway map used in all the models.

\subsection*{Antoine}
Implemented the MaxFlow and Markov models. Created almost all of the graph and network visualizations. Worked on the two first models' analyses for the manuscript. Wrote the Future Work section and the Individual Contributions.
